---
title: "Reset to 2019-04 RNASeq Analysis Parameters"
author: "Trevor Randall"
date: "25/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set Lib install location for Desktop
```{r, eval = TRUE}
.libPaths(c("L:/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))
PackRatLibLocations <- file.path("L:/RStudios/RPackRat_2019_04_DESEQLibs")
```

#Set Lib install location for Laptop
```{r, eval = FALSE}
.libPaths("") 
PackRatLibLocations <- file.path("")
```


#Package loadng
```{r}
library("yaml", lib.loc = PackRatLibLocations)
```

#Note that R version = 3.5.1

```{r}
#Installation of CRAN Packages
install.packages("devtools")
library(devtools)
withr::with_libpaths(new = PackRatLibLocations, code = install_version("foreach", version = "1.4.4", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("bit64", version = "0.9-7", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("Formula", version = "1.2-3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("assertthat", version = "0.2.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("mixsqp", version = "0.1-97", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("latticeExtra", version = "0.6-28", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("blob", version = "1.1.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("yaml", version = "2.2.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("numDeriv", version = "2016.8-1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("pillar", version = "1.3.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("RSQLite", version = "2.1.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("backports", version = "1.1.3",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("lattice", version = "0.20-38",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("bbmle", version = "1.0.20",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("digest", version = "0.6.18",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("RColorBrewer", version = "1.1-2",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("checkmate", version = "1.9.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("colorspace", version = "1.4-0",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("htmltools", version = "0.3.6",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("Matrix", version = "1.2-16",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("plyr", version = "1.8.4",  upgrade = "never"))
install_version("XML", version = "3.98-1.19",  upgrade = "never")
withr::with_libpaths(new = PackRatLibLocations, code = install_version("pkgconfig", version = "2.0.2",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("emdbook", version = "1.3.11",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("xtable", version = "1.8-3",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("scales", version = "1.0.0",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("htmlTable", version = "1.13.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("tibble", version = "2.1.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("ggplot2", version = "3.1.0",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("ashr", version = "2.2-32",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("nnet", version = "7.3-12",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("lazyeval", version = "0.2.2",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("survival", version = "2.43-3",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("magrittr", version = "1.5",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("crayon", version = "1.3.4",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("memoise", version = "1.1.0",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("doParallel", version = "1.0.14",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("MASS", version = "7.3-51.1",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("truncnorm", version = "1.0-8",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("foreign", version = "0.8-71",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("data.table", version = "1.12.0",  upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("stringr", version = "1.4.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("munsell", version = "0.5.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("locfit", version = "1.5-9.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("cluster", version = "2.0.7-1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("Rcpp", version = "1.0.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("iterators", version = "1.0.10", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("rstudioapi", version = "0.10", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("htmlwidgets", version = "1.3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("bitops", version = "1.0-6", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("base64enc", version = "0.1-3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("codetools", version = "0.2-16", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("gtable", version = "0.2.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("DBI", version = "1.0.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("R6", version = "2.4.0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("gridExtra", version = "2.3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("knitr", version = "1.22", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("bit", version = "1.1-14", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("Hmisc", version = "4.2-0", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("pscl", version = "1.5.2", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("stringi", version = "1.4.3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("SQUAREM", version = "2017.10-1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("rpart", version = "4.1-13", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("acepack", version = "1.4.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("xfun", version = "0.5", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("coda", version = "0.19-2", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("readr", version = "1.3.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("VennDiagram", version = "1.6.20", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("gridExtra", version = "2.3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("futile.logger", version = "1.4.3", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("futile.options", version = "1.0.1", upgrade = "never"))
withr::with_libpaths(new = PackRatLibLocations, code = install_version("pkgconfig", version = "2.0.2", upgrade = "never"))


#Ignore if same results
#withr::with_libpaths(new = PackRatLibLocations, code = install_version("FormatR", version = "1.6", upgrade = "never"))
#withr::with_libpaths(new = PackRatLibLocations, code = install_version("hms", version = "0.4.2", upgrade = "never"))
#withr::with_libpaths(new = PackRatLibLocations, code = install_version("lambda.r", version = "1.2.3", upgrade = "never"))
```



#Packages that appear to already be installed directly through R
```{r}
#install_version("grid", version = "3.5.1") #Preinstalled.... System Tool?
#install_version("compiler", version = "3.5.1")  #Preinstalled.... System Tool?
#install_version("tools", version = "3.5.1") #Preinstalled.... System Tool?
#withr::with_libpaths(new = PackRatLibLocations, code = install_version("splines", version = "3.5.1", upgrade = "never"))
```

#Packages that do not appear to be in the Cran DB
```{r, eval=FALSE}
#install_version("GenomeInfoDbData", version = "1.1.0") #Where is this from
```

#Packages that the righ version appears unable to be found
```{r, eval=FALSE}
#install_version("rlang", version = "0.3.1") #From Bioconductor? #Downloadign through CRAN, but failing to install #Is this Important?
#install_version("RCurl", version = "1.95-4.12") #From Bioconductor? #Downloadign through CRAN, but failing to install #Is this Important?
```

#Installation of Bioconductor and Packages
```{r}
source("https://bioconductor.org/biocLite.R")
biocLite("AnnotationDbi", version = "1.42.1", suppressUpdates = TRUE)
biocLite("XVector", version = "0.20.0", suppressUpdates = TRUE)
biocLite("genefilter", version = "1.62.0", suppressUpdates = TRUE)
biocLite("zlibbioc", version = "1.26.0", suppressUpdates = TRUE)
biocLite("apeglm", version = "1.2.1", suppressUpdates = TRUE)
biocLite("annotate", version = "1.58.0", suppressUpdates = TRUE)
biocLite("geneplotter", version = "1.58.0", suppressUpdates = TRUE)
biocLite("AnnotationDbi", version = "1.42.1", suppressUpdates = TRUE)

biocLite("DESeq2", version = "1.20.0", suppressUpdates = TRUE)
biocLite("SummarizedExperiment", version = "1.10.1", suppressUpdates = TRUE)
biocLite("DelayedArray", version = "0.6.6", suppressUpdates = TRUE)
biocLite("BiocParallel", version = "1.14.2", suppressUpdates = TRUE)
biocLite("matrixStats", version = "0.54.0", suppressUpdates = TRUE)
biocLite("Biobase", version = "2.40.0", suppressUpdates = TRUE)
biocLite("GenomicRanges", version = "1.32.7", suppressUpdates = TRUE)
biocLite("GenomeInfoDb", version = "1.16.0", suppressUpdates = TRUE)
biocLite("IRanges", version = "2.14.12", suppressUpdates = TRUE)
#biocLite("S4Vectors", version = "0.18.3", suppressUpdates = TRUE)
biocLite("S4Vectors", version = "0.19.11", suppressUpdates = TRUE)
biocLite("BiocGenerics", version = "0.26.0", suppressUpdates = TRUE)
biocLite("ComplexHeatmap", version)
```

```


#Installation of packages for Volcano plot analysis
```{r}
library(devtools)
withr::with_libpaths(new = PackRatLibLocations, code = install_version("ggrepel", upgrade = "never"))
```


#Install GenomeInfoDbData from source Package
```{r}
install.packages("E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/Source Packages/GenomeInfoDbData_1.2.0.tar.gz", repos = NULL, type="source")

install.packages('E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/Source Packages/EnhancedVolcano_1.6.0.zip', repos = NULL)
```


