---
title: "Isolating DE Genes from Expression analysis"
author: "Trevor Randall"
date: "February 27, 2019"
output:
  word_document: default
  html_document: default
---
## Initial environment setup (Code Block 1)
```{r setup, include=TRUE, eval=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clear Global Environment (Code Block 2)
```{r, eval=FALSE}
remove(list = ls())
```

## Set all library paths and load the required libraries (Code Block 3)
```{r, eval=FALSE}
#Set Library Directory
#PC Path
.libPaths(c("<SetLibraryLocations>/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))

#Set working directory
#PC Path
setwd("<SetWorkingLibraryLocation>/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/CF39vsCF39S/Pure Temperature Analysis Comparisons/")
```

## Libraries to install (Code Block 4)
```{r, eval=FALSE}
install.packages('VennDiagram')
```

## Libraries to open (Code Block 5)
```{r, eval=FALSE}
library(readr)
library(VennDiagram)
```

## Opening Preprocessed Datasets (Code Block 6)

```{r, eval=FALSE}
TDESEQList_25vs25 <- read_delim("../25 vs 25/DE_Reg_Genes_Analysis/TDESEQ25vs25.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_25vs25) <- c("locus", "baseMean", "log2FoldChange_25C", "lfcSE", "stat", "pvalue_25C", "padj_25C", "gene_name", "gene_discription", "raw_locus")

TDESEQList_29vs29 <- read_delim("../29 vs 29/DE_Reg_Genes_Analysis/TDESEQ29vs29.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_29vs29) <- c("locus", "baseMean", "log2FoldChange_29C", "lfcSE", "stat", "pvalue_29C", "padj_29C", "gene_name", "gene_discription", "raw_locus")

TDESEQList_33vs33 <- read_delim("../33 vs 33/DE_Reg_Genes_Analysis/TDESEQ33vs33.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_33vs33) <- c("locus", "baseMean", "log2FoldChange_33C", "lfcSE", "stat", "pvalue_33C", "padj_33C", "gene_name", "gene_discription", "raw_locus")

TDESEQList_37vs37 <- read_delim("../37 vs 37/DE_Reg_Genes_Analysis/TDESEQ37vs37.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_37vs37) <- c("locus", "baseMean", "log2FoldChange_37C", "lfcSE", "stat", "pvalue_37C", "padj_37C", "gene_name", "gene_discription", "raw_locus")

TDESEQList_41vs41 <- read_delim("../41 vs 41/DE_Reg_Genes_Analysis/TDESEQ41vs41.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_41vs41) <- c("locus", "baseMean", "log2FoldChange_41C", "lfcSE", "stat", "pvalue_41C", "padj_41C", "gene_name", "gene_discription", "raw_locus")
```


## Convert Log2Fold Change to Fold Change (Code Block 7)
```{r, eval=FALSE}
TDESEQList_25vs25$FoldChange_25 <- ifelse(((TDESEQList_25vs25$log2FoldChange_25C) >= 0), (2^TDESEQList_25vs25$log2FoldChange_25C), (-1/(2^TDESEQList_25vs25$log2FoldChange_25C)))

ColOrder25 <- c("locus", "baseMean", "log2FoldChange_25C", "FoldChange_25", "lfcSE", "stat", "pvalue_25C", "padj_25C", "gene_name", "gene_discription", "raw_locus")
TDESEQList_25vs25 <- TDESEQList_25vs25[, ColOrder25]


TDESEQList_29vs29$FoldChange_29 <- ifelse(((TDESEQList_29vs29$log2FoldChange_29C) >= 0), (2^TDESEQList_29vs29$log2FoldChange_29C), (-1/(2^TDESEQList_29vs29$log2FoldChange_29C)))

ColOrder29 <- c("locus", "baseMean", "log2FoldChange_29C", "FoldChange_29", "lfcSE", "stat", "pvalue_29C", "padj_29C", "gene_name", "gene_discription", "raw_locus")
TDESEQList_29vs29 <- TDESEQList_29vs29[, ColOrder29]


TDESEQList_33vs33$FoldChange_33 <- ifelse(((TDESEQList_33vs33$log2FoldChange_33C) >= 0), (2^TDESEQList_33vs33$log2FoldChange_33C), (-1/(2^TDESEQList_33vs33$log2FoldChange_33C)))

ColOrder33 <- c("locus", "baseMean", "log2FoldChange_33C", "FoldChange_33", "lfcSE", "stat", "pvalue_33C", "padj_33C", "gene_name", "gene_discription", "raw_locus")
TDESEQList_33vs33 <- TDESEQList_33vs33[, ColOrder33]


TDESEQList_37vs37$FoldChange_37 <- ifelse(((TDESEQList_37vs37$log2FoldChange_37C) >= 0), (2^TDESEQList_37vs37$log2FoldChange_37C), (-1/(2^TDESEQList_37vs37$log2FoldChange_37C)))

ColOrder37 <- c("locus", "baseMean", "log2FoldChange_37C", "FoldChange_37", "lfcSE", "stat", "pvalue_37C", "padj_37C", "gene_name", "gene_discription", "raw_locus")
TDESEQList_37vs37 <- TDESEQList_37vs37[, ColOrder37]


TDESEQList_41vs41$FoldChange_41 <- ifelse(((TDESEQList_41vs41$log2FoldChange_41C) >= 0), (2^TDESEQList_41vs41$log2FoldChange_41C), (-1/(2^TDESEQList_41vs41$log2FoldChange_41C)))

ColOrder41 <- c("locus", "baseMean", "log2FoldChange_41C", "FoldChange_41", "lfcSE", "stat", "pvalue_41C", "padj_41C", "gene_name", "gene_discription", "raw_locus")
TDESEQList_41vs41 <- TDESEQList_41vs41[, ColOrder41]
```


## Saving correct format for each table (Code Block 8)
```{r, eval=FALSE}
write.table(x = TDESEQList_25vs25, file="./OriginalFiles/TDESEQList_25vs25_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_25vs25), quote=F)

write.table(x = TDESEQList_29vs29, file="./OriginalFiles/TDESEQList_29vs29_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_29vs29), quote=F)

write.table(x = TDESEQList_33vs33, file="./OriginalFiles/TDESEQList_33vs33_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_33vs33), quote=F)

write.table(x = TDESEQList_37vs37, file="./OriginalFiles/TDESEQList_37vs37_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_37vs37), quote=F)

write.table(x = TDESEQList_41vs41, file="./OriginalFiles/TDESEQList_41vs41_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_41vs41), quote=F)
```


# Parcing patterns from files
P designation is temperature pure (so for instance CF3925vsCF39S25 is P25 or CF3929vsCF39S29 is P29)

## Identify trends from P25 to P29 (Code Block 9)
```{r, eval=FALSE}
P25vsP29_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_29vs29$locus), ]

P25_DiffGenesToP29 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_25vs25$padj_25C))), ]

P29_DiffGenesToP25 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_29vs29$padj_29C))),]
```

## Identify trends from P25 to P33 (Code Block 10)
```{r, eval=FALSE}
P25vsP33_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_33vs33$locus), ]

P25_DiffGenesToP33 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_25vs25$padj_25C))), ]

P33_DiffGenesToP25 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_33vs33$padj_33C))),]
```


## Identify trends from P25 to P37 (Code Block 11)
```{r, eval=FALSE}
P25vsP37_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_37vs37$locus), ]

P25_DiffGenesToP37 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_25vs25$padj_25C))), ]

P37_DiffGenesToP25 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_37vs37$padj_37C))),]
```
 
## Identify trends from P25 to P41 (Code Block 12)
```{r, eval=FALSE}
P25vsP41_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_41vs41$locus), ]

P25_DiffGenesToP41 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_25vs25$padj_25C))), ]

P41_DiffGenesToP25 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_41vs41$padj_41C))),]
```

## Identify trends from P29 to P33 (Code Block 13)
```{r, eval=FALSE}
P29vsP33_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_33vs33$locus), ]

P29_DiffGenesToP33 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_29vs29$padj_29C))), ]

P33_DiffGenesToP29 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_33vs33$padj_33C))),]
```

## Identify trends from P29 to P37 (Code Block 14)
```{r, eval=FALSE}
P29vsP37_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_37vs37$locus), ]

P29_DiffGenesToP37 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_29vs29$padj_29C))), ]

P37_DiffGenesToP29 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_37vs37$padj_37C))),]
```

## Identify trends from P29 to P41 (Code Block 15)
```{r, eval=FALSE}
P29vsP41_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_41vs41$locus), ]

P29_DiffGenesToP41 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_29vs29$padj_29C))), ]

P41_DiffGenesToP29 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_41vs41$padj_41C))),]
```

## Identify trends from P33 to P37 (Code Block 16)
```{r, eval=FALSE}
P33vsP37_SameGenes<- TDESEQList_33vs33[(TDESEQList_33vs33$locus %in% TDESEQList_37vs37$locus), ]

P33_DiffGenesToP37 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_33vs33$padj_33C))), ]

P37_DiffGenesToP33 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_37vs37$padj_37C))),]
```

## Identify trends from P33 to P41 (Code Block 17)
```{r, eval=FALSE}
P33vsP41_SameGenes<- TDESEQList_33vs33[(TDESEQList_33vs33$locus %in% TDESEQList_41vs41$locus), ]

P33_DiffGenesToP41 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_33vs33$padj_33C))), ]

P41_DiffGenesToP33 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_41vs41$padj_41C))),]
```

## Identify trends from P37 to P41 (Code Block 18)
```{r, eval=FALSE}
P37vsP41_SameGenes<- TDESEQList_37vs37[(TDESEQList_37vs37$locus %in% TDESEQList_41vs41$locus), ]

P37_DiffGenesToP41 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_37vs37$padj_37C))), ]

P41_DiffGenesToP37 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_41vs41$padj_41C))),]
```

## Combine full files (Code Block 19)
```{r, eval=FALSE}
LocusGeneAssociation <- read_csv("../SourceRNASEQCountsForDESEQ/Locus_GeneNamesAndPredictedFunction.csv")

Combined_List <- 0
Combined_List <- merge(TDESEQList_25vs25, y = TDESEQList_29vs29, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_33vs33, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_37vs37, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_41vs41, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
```

# Reformat Files
## Shrink All (Code Block 20)
```{r, eval=FALSE}
ColToRemove <- c("baseMean", "lfcSE", "stat", "gene_name", "gene_discription", "raw_locus")

TDESEQList_25vs25_Shrunk <- TDESEQList_25vs25[, !names(TDESEQList_25vs25) %in% ColToRemove, drop = F]
TDESEQList_29vs29_Shrunk <- TDESEQList_29vs29[, !names(TDESEQList_29vs29) %in% ColToRemove, drop = F]
TDESEQList_33vs33_Shrunk <- TDESEQList_33vs33[, !names(TDESEQList_33vs33) %in% ColToRemove, drop = F]
TDESEQList_37vs37_Shrunk <- TDESEQList_37vs37[, !names(TDESEQList_37vs37) %in% ColToRemove, drop = F]
TDESEQList_41vs41_Shrunk <- TDESEQList_41vs41[, !names(TDESEQList_41vs41) %in% ColToRemove, drop = F]
```

## Combine shrunk files (Code Block 21)
```{r, eval=FALSE}
LocusGeneAssociation <- read_csv("../SourceRNASEQCountsForDESEQ/Locus_GeneNamesAndPredictedFunction.csv")

Combined_List_Shrunk <- 0
Combined_List_Shrunk <- merge(TDESEQList_25vs25_Shrunk, y = TDESEQList_29vs29_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_33vs33_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_37vs37_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_41vs41_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, LocusGeneAssociation, by = "locus")

write.table(x = Combined_List_Shrunk, file="./Combined List Analysis Shrunk.txt", sep="\t", row.names=FALSE, col.names=colnames(Combined_List_Shrunk), quote=F)
```

## (Code Block 22)
Remove Igbot/Igtop form analysis
Remove igtop/igbot from analysis
Remove Unwanted Columns
```{r, eval=FALSE}
ColToRemove <- c("baseMean", "lfcSE", "stat", "gene", "product", "locusNumber")

Combined_List_Shrunk2_Full <- Combined_List_Shrunk[, !names(Combined_List_Shrunk) %in% ColToRemove, drop = F]
Combined_List_Shrunk2TailListSense <- Combined_List_Shrunk2_Full[((grep((glob2rx('*_sense')), Combined_List_Shrunk2_Full$locus))), ]
Combined_List_Shrunk2TailListAntiSense <- Combined_List_Shrunk2_Full[((grep((glob2rx('*_antis')), Combined_List_Shrunk2_Full$locus))), ]
Combined_List_Shrunk2TailListMerged <- rbind(Combined_List_Shrunk2TailListSense, Combined_List_Shrunk2TailListAntiSense)
Combined_List_Shrunk2 <- Combined_List_Shrunk2TailListMerged[order(Combined_List_Shrunk2TailListMerged$locus), ]
Combined_List_Shrunk2 <- merge(Combined_List_Shrunk2, LocusGeneAssociation, by = "locus")

write.table(x = Combined_List_Shrunk2, file="./Combined List Analysis Shrunk2.txt", sep="\t", row.names=FALSE, col.names=colnames(Combined_List_Shrunk2), quote=F)
```


## Session Info (Code Block 23)
```{r, eval=FALSE}
sink(file = "./SessionInfo.txt")
sessionInfo()
sink(file = NULL)
```

## Citations (Code Block 24)
```{r, eval=FALSE}
sink(file = "./SessionCitations.txt")

citation("VennDiagram")
citation("readr")
citation("gridExtra")

sink(file = NULL)
```

Venn Diagram Page: https://rstudio-pubs-static.s3.amazonaws.com/13301_6641d73cfac741a59c0a851feb99e98b.html?fbclid=IwAR1h2pL9V1tblTk4z9E1JX9udrel2ILE_WKKp2M8Kjd6HB0ZC6wwctFu61Y
