---
title: "Isolating DE Genes from Expression analysis"
author: "Trevor Randall"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries to install:
```{r, eval=FALSE}
install.packages('VennDiagram')
```


Libraries to open:
```{r}
library(readr)
library(VennDiagram)
```


```{r}
#Set Library Directory
#PC Path
.libPaths(c("L:/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))

#Set working directory
#PC Path
setwd("E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/CF39vsCF39S/Pure Temperature Analysis Comparisons/")
#Laptop Path
#Set Library Directory
#.libPaths(c(""))
#setwd("")
#sink(file = "./RSessionRawRun.txt") 
```

#Opening Preprocessed Datasets

```{r}
TDESEQList_25vs25 <- read_delim("../25 vs 25/DE_Reg_Genes_Analysis/TDESEQ25vs25.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_25vs25) <- c("locus", "baseMean", "log2FoldChange_25C", "lfcSE", "stat", "pvalue_25C", "padj_Temp", "gene_name", "gene_discription", "raw_locus")

TDESEQList_29vs29 <- read_delim("../29 vs 29/DE_Reg_Genes_Analysis/TDESEQ29vs29.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_29vs29) <- c("locus", "baseMean", "log2FoldChange_29C", "lfcSE", "stat", "pvalue_29C", "padj_Temp", "gene_name", "gene_discription", "raw_locus")

TDESEQList_33vs33 <- read_delim("../33 vs 33/DE_Reg_Genes_Analysis/TDESEQ33vs33.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_33vs33) <- c("locus", "baseMean", "log2FoldChange_33C", "lfcSE", "stat", "pvalue_33C", "padj_Temp", "gene_name", "gene_discription", "raw_locus")

TDESEQList_37vs37 <- read_delim("../37 vs 37/DE_Reg_Genes_Analysis/TDESEQ37vs37.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_37vs37) <- c("locus", "baseMean", "log2FoldChange_37C", "lfcSE", "stat", "pvalue_37C", "padj_Temp", "gene_name", "gene_discription", "raw_locus")

TDESEQList_41vs41 <- read_delim("../41 vs 41/DE_Reg_Genes_Analysis/TDESEQ41vs41.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESEQList_41vs41) <- c("locus", "baseMean", "log2FoldChange_41C", "lfcSE", "stat", "pvalue_41C", "padj_Temp", "gene_name", "gene_discription", "raw_locus")
```

#Saving correct format for each table
```{r}
write.table(x = TDESEQList_25vs25, file="./OriginalFiles/TDESEQList_25vs25_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_25vs25), quote=F)

write.table(x = TDESEQList_29vs29, file="./OriginalFiles/TDESEQList_29vs29_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_29vs29), quote=F)

write.table(x = TDESEQList_33vs33, file="./OriginalFiles/TDESEQList_33vs33_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_33vs33), quote=F)

write.table(x = TDESEQList_37vs37, file="./OriginalFiles/TDESEQList_37vs37_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_37vs37), quote=F)

write.table(x = TDESEQList_41vs41, file="./OriginalFiles/TDESEQList_41vs41_Original.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQList_41vs41), quote=F)
```




#Parcing patterns from files
P designation is temperature pure (so for instance CF3925vsCF39S25 is P25 or CF3929vsCF39S29 is P29)

##Identify trends from P25 to P29
```{r}
P25vsP29_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_29vs29$locus), ]

P25_DiffGenesToP29 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_25vs25$padj))), ]

P29_DiffGenesToP25 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_29vs29$padj))),]


```

##Identify trends from P25 to P33
```{r}
P25vsP33_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_33vs33$locus), ]

P25_DiffGenesToP33 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_25vs25$padj))), ]

P33_DiffGenesToP25 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_33vs33$padj))),]
```


##Identify trends from P25 to P37
```{r}
P25vsP37_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_37vs37$locus), ]

P25_DiffGenesToP37 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_25vs25$padj))), ]

P37_DiffGenesToP25 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_37vs37$padj))),]
```

##Identify trends from P25 to P41
```{r}
P25vsP41_SameGenes<- TDESEQList_25vs25[(TDESEQList_25vs25$locus %in% TDESEQList_41vs41$locus), ]

P25_DiffGenesToP41 <- TDESEQList_25vs25[!((TDESEQList_25vs25$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_25vs25$padj))), ]

P41_DiffGenesToP25 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_25vs25$locus)& (!is.na(TDESEQList_41vs41$padj))),]
```

##Identify trends from P29 to P33
```{r}
P29vsP33_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_33vs33$locus), ]

P29_DiffGenesToP33 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_29vs29$padj))), ]

P33_DiffGenesToP29 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_33vs33$padj))),]
```

##Identify trends from P29 to P37
```{r}
P29vsP37_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_37vs37$locus), ]

P29_DiffGenesToP37 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_29vs29$padj))), ]

P37_DiffGenesToP29 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_37vs37$padj))),]
```

##Identify trends from P29 to P41
```{r}
P29vsP41_SameGenes<- TDESEQList_29vs29[(TDESEQList_29vs29$locus %in% TDESEQList_41vs41$locus), ]

P29_DiffGenesToP41 <- TDESEQList_29vs29[!((TDESEQList_29vs29$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_29vs29$padj))), ]

P41_DiffGenesToP29 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_29vs29$locus)& (!is.na(TDESEQList_41vs41$padj))),]
```

##Identify trends from P33 to P37
```{r}
P33vsP37_SameGenes<- TDESEQList_33vs33[(TDESEQList_33vs33$locus %in% TDESEQList_37vs37$locus), ]

P33_DiffGenesToP37 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_33vs33$padj))), ]

P37_DiffGenesToP33 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_37vs37$padj))),]
```

##Identify trends from P33 to P41
```{r}
P33vsP41_SameGenes<- TDESEQList_33vs33[(TDESEQList_33vs33$locus %in% TDESEQList_41vs41$locus), ]

P33_DiffGenesToP41 <- TDESEQList_33vs33[!((TDESEQList_33vs33$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_33vs33$padj))), ]

P41_DiffGenesToP33 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_33vs33$locus)& (!is.na(TDESEQList_41vs41$padj))),]
```

##Identify trends from P37 to P41
```{r}
P37vsP41_SameGenes<- TDESEQList_37vs37[(TDESEQList_37vs37$locus %in% TDESEQList_41vs41$locus), ]

P37_DiffGenesToP41 <- TDESEQList_37vs37[!((TDESEQList_37vs37$locus %in% TDESEQList_41vs41$locus)& (!is.na(TDESEQList_37vs37$padj))), ]

P41_DiffGenesToP37 <- TDESEQList_41vs41[!((TDESEQList_41vs41$locus %in% TDESEQList_37vs37$locus)& (!is.na(TDESEQList_41vs41$padj))),]
```

#Combine full files
```{r}
LocusGeneAssociation <- read_csv("../SourceRNASEQCountsForDESEQ/Locus_GeneNamesAndPredictedFunction.csv")


Combined_List <- 0
Combined_List <- merge(TDESEQList_25vs25, y = TDESEQList_29vs29, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_33vs33, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_37vs37, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List <- merge(Combined_List, y = TDESEQList_41vs41, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
```

#Reformat Files
##Shrink All
```{r}
ColToRemove <- c("baseMean", "lfcSE", "stat", "padj_Temp", "gene_name", "gene_discription", "raw_locus")

TDESEQList_25vs25_Shrunk <- TDESEQList_25vs25[, !names(TDESEQList_25vs25) %in% ColToRemove, drop = F]
TDESEQList_29vs29_Shrunk <- TDESEQList_29vs29[, !names(TDESEQList_29vs29) %in% ColToRemove, drop = F]
TDESEQList_33vs33_Shrunk <- TDESEQList_33vs33[, !names(TDESEQList_33vs33) %in% ColToRemove, drop = F]
TDESEQList_37vs37_Shrunk <- TDESEQList_37vs37[, !names(TDESEQList_37vs37) %in% ColToRemove, drop = F]
TDESEQList_41vs41_Shrunk <- TDESEQList_41vs41[, !names(TDESEQList_41vs41) %in% ColToRemove, drop = F]
```

#Combine shrunk files
```{r}
LocusGeneAssociation <- read_csv("../SourceRNASEQCountsForDESEQ/Locus_GeneNamesAndPredictedFunction.csv")


Combined_List_Shrunk <- 0
Combined_List_Shrunk <- merge(TDESEQList_25vs25_Shrunk, y = TDESEQList_29vs29_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_33vs33_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_37vs37_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, y = TDESEQList_41vs41_Shrunk, by.x= "locus", by.y = "locus", all.x = T, all.y = T)
Combined_List_Shrunk <- merge(Combined_List_Shrunk, LocusGeneAssociation, by = "locus")

write.table(x = Combined_List_Shrunk, file="./Combined List Analysis Shrunk.txt", sep="\t", row.names=FALSE, col.names=colnames(Combined_List_Shrunk), quote=F)
```



#Session Info
```{r}
sink(file = "./SessionInfo.txt")
sessionInfo()
sink(file = NULL)
```


#Citations
```{r}
sink(file = "./SessionCitations.txt")

citation("VennDiagram")
citation("readr")
citation("gridExtra")

sink(file = NULL)
```

Venn Diagram Page: https://rstudio-pubs-static.s3.amazonaws.com/13301_6641d73cfac741a59c0a851feb99e98b.html?fbclid=IwAR1h2pL9V1tblTk4z9E1JX9udrel2ILE_WKKp2M8Kjd6HB0ZC6wwctFu61Y
