---
title: "VolcanoPlot Analysis Pure Temp Analysis"
author: "Trevor Randall"
date: "07/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Clear Global Environment
```{r}
remove(list = ls())
```


```{r}
#Set Library Directory
#PC Path
.libPaths(c("L:/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))

#Set working directory
#PC Path
setwd("E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/CF39vsCF39S/Pure Temperature Analysis Comparisons/VolcanoPlots/")
#Laptop Path
#Set Library Directory
#.libPaths(c(""))
#setwd("")
#sink(file = "./RSessionRawRun.txt") 
```


Libraries to install:
```{r, eval=FALSE}
install.packages('E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/Source Packages/EnhancedVolcano_1.6.0.zip', repos = NULL)
```


Libraries to open:
```{r}
library(readr)
library(ggplot2)
library(EnhancedVolcano)
```


#Opening Preprocessed Datasets
```{r}
LCFShrinkResults25vs25_apeglm <- read_delim("../../25 vs 25/My DESEQ Script/DESeq_results_LCFShrinkResults-apeglm.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults25vs25_normal <- read_delim("../../25 vs 25/My DESEQ Script/DESeq_results_LCFShrinkResults-normal.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults25vs25_ashr <- read_delim("../../25 vs 25/My DESEQ Script/DESeq_results_LCFShrinkResults-ashr.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults29vs29_apeglm <- read_delim("../../29 vs 29/My DESEQ Script/DESeq_results_LCFShrinkResults-apeglm.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults29vs29_normal <- read_delim("../../29 vs 29/My DESEQ Script/DESeq_results_LCFShrinkResults-normal.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults29vs29_ashr <- read_delim("../../29 vs 29/My DESEQ Script/DESeq_results_LCFShrinkResults-ashr.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults33vs33_apeglm <- read_delim("../../33 vs 33/My DESEQ Script/DESeq_results_LCFShrinkResults-apeglm.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults33vs33_normal <- read_delim("../../33 vs 33/My DESEQ Script/DESeq_results_LCFShrinkResults-normal.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults33vs33_ashr <- read_delim("../../33 vs 33/My DESEQ Script/DESeq_results_LCFShrinkResults-ashr.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults37vs37_apeglm <- read_delim("../../37 vs 37/My DESEQ Script/DESeq_results_LCFShrinkResults-apeglm.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults37vs37_normal <- read_delim("../../37 vs 37/My DESEQ Script/DESeq_results_LCFShrinkResults-normal.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults37vs37_ashr <- read_delim("../../37 vs 37/My DESEQ Script/DESeq_results_LCFShrinkResults-ashr.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults41vs41_apeglm <- read_delim("../../41 vs 41/My DESEQ Script/DESeq_results_LCFShrinkResults-apeglm.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults41vs41_normal <- read_delim("../../41 vs 41/My DESEQ Script/DESeq_results_LCFShrinkResults-normal.txt", "\t", escape_double = FALSE, trim_ws = TRUE)

LCFShrinkResults41vs41_ashr <- read_delim("../../41 vs 41/My DESEQ Script/DESeq_results_LCFShrinkResults-ashr.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
```

#25C Volcano Plots

##Creating Vocano Plots for apeglm dataset
```{r}
apeglmVPlot25vs25 <- EnhancedVolcano(LCFShrinkResults25vs25_apeglm, 
                lab = '', # LCFShrinkResults25vs25_apeglm$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )


##Save Volcano Plot

dev.off()
png(filename = "./apeglm Volcano Plot 25vs25.png",width = 11, height = 9, res = 300, units = "in")

apeglmVPlot25vs25

par(mfrow = c(1,1)) # Good practice to immediatly reset plot sizing

dev.off()
```

##Creating Vocano Plots for normal dataset
```{r}
NormalVPlot25vs25 <- EnhancedVolcano(LCFShrinkResults25vs25_normal, 
                lab = '', # LCFShrinkResults25vs25_normal$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./Normal Volcano Plot 25vs25.png",width = 11, height = 9, res = 300, units = "in")

NormalVPlot25vs25

par(mfrow = c(1,1)) # Good practice to immediatly reset plot sizing

dev.off()
```

##Creating Vocano Plots for apeglm dataset
```{r}
ashrVPlot25vs25 <- EnhancedVolcano(LCFShrinkResults25vs25_ashr, 
                lab = '', # LCFShrinkResults25vs25_ashr$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./AshR Volcano Plot 25vs25.png",width = 11, height = 9, res = 300, units = "in")

ashrVPlot25vs25

par(mfrow = c(1,1)) # Good practice to immediatly reset plot sizing

dev.off()
```

#29C Volcano Plots

##Creating Vocano Plots for apeglm dataset
```{r}
apeglmVPlot29vs29 <- EnhancedVolcano(LCFShrinkResults29vs29_apeglm, 
                lab = '', # LCFShrinkResults29vs29_apeglm$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./apeglm Volcano Plot 29vs29.png",width = 11, height = 9, res = 300, units = "in")

apeglmVPlot29vs29

par(mfrow = c(1,1)) # Good practice to immediatly reset plot sizing

dev.off()
```

##Creating Vocano Plots for normal dataset
```{r}
NormalVPlot29vs29 <- EnhancedVolcano(LCFShrinkResults29vs29_normal, 
                lab = '', # LCFShrinkResults29vs29_normal$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./Normal Volcano Plot 29vs29.png",width = 11, height = 9, res = 300, units = "in")

NormalVPlot29vs29

par(mfrow = c(1,1)) # Good practice to immediatly reset plot sizing

dev.off()
```

##Creating Vocano Plots for apeglm dataset
```{r}
ashrVPlot29vs29 <- EnhancedVolcano(LCFShrinkResults29vs29_ashr, 
                lab = '', # LCFShrinkResults29vs29_ashr$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./AshR Volcano Plot 29vs29.png",width = 11, height = 9, res = 300, units = "in")

ashrVPlot29vs29

par(mfrow = c(1,1))

dev.off()
```

#33C Volcano Plots

##Creating Vocano Plots for apeglm dataset
```{r}
apeglmVPlot33vs33 <- EnhancedVolcano(LCFShrinkResults33vs33_apeglm, 
                lab = '', # LCFShrinkResults33vs33_apeglm$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./apeglm Volcano Plot 33vs33.png",width = 11, height = 9, res = 300, units = "in")

apeglmVPlot33vs33

par(mfrow = c(1,1))

dev.off()
```

##Creating Vocano Plots for normal dataset
```{r}
NormalVPlot33vs33 <- EnhancedVolcano(LCFShrinkResults33vs33_normal, 
                lab = '', # LCFShrinkResults33vs33_normal$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./Normal Volcano Plot 33vs33.png",width = 11, height = 9, res = 300, units = "in")

NormalVPlot33vs33

par(mfrow = c(1,1))

dev.off()
```

##Creating Vocano Plots for apeglm dataset
```{r}
ashrVPlot33vs33 <- EnhancedVolcano(LCFShrinkResults33vs33_ashr, 
                lab = '', # LCFShrinkResults33vs33_ashr$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./AshR Volcano Plot 33vs33.png",width = 11, height = 9, res = 300, units = "in")

ashrVPlot33vs33

par(mfrow = c(1,1))

dev.off()
```


#37C Volcano Plots

##Creating Vocano Plots for apeglm dataset
```{r}
apeglmVPlot37vs37 <- EnhancedVolcano(LCFShrinkResults37vs37_apeglm, 
                lab = '', # LCFShrinkResults37vs37_apeglm$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./apeglm Volcano Plot 37vs37.png",width = 11, height = 9, res = 300, units = "in")

apeglmVPlot37vs37

par(mfrow = c(1,1))

dev.off()


```

##Creating Vocano Plots for normal dataset
```{r}
NormalVPlot37vs37 <- EnhancedVolcano(LCFShrinkResults37vs37_normal, 
                lab = '', # LCFShrinkResults37vs37_normal$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./Normal Volcano Plot 37vs37.png",width = 11, height = 9, res = 300, units = "in")

NormalVPlot37vs37

par(mfrow = c(1,1)) 

dev.off()
```

##Creating Vocano Plots for apeglm dataset
```{r}
ashrVPlot37vs37 <- EnhancedVolcano(LCFShrinkResults37vs37_ashr, 
                lab = '', # LCFShrinkResults37vs37_ashr$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./AshR Volcano Plot 37vs37.png",width = 11, height = 9, res = 300, units = "in")

ashrVPlot37vs37

par(mfrow = c(1,1))

dev.off()
```


#41C Volcano Plots

##Creating Vocano Plots for apeglm dataset
```{r}
apeglmVPlot41vs41 <- EnhancedVolcano(LCFShrinkResults41vs41_apeglm, 
                lab = '', # LCFShrinkResults41vs41_apeglm$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./apeglm Volcano Plot 41vs41.png",width = 11, height = 9, res = 300, units = "in")

apeglmVPlot41vs41

par(mfrow = c(1,1))

dev.off()

```

##Creating Vocano Plots for normal dataset
```{r}
NormalVPlot41vs41 <- EnhancedVolcano(LCFShrinkResults41vs41_normal, 
                lab = '', # LCFShrinkResults41vs41_normal$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./Normal Volcano Plot 41vs41.png",width = 11, height = 9, res = 300, units = "in")

NormalVPlot41vs41

par(mfrow = c(1,1))

dev.off()
```

##Creating Vocano Plots for apeglm dataset
```{r}
ashrVPlot41vs41 <- EnhancedVolcano(LCFShrinkResults41vs41_ashr, 
                lab = '', # LCFShrinkResults41vs41_ashr$locus,
                x = 'log2FoldChange',
                y = 'padj',
                xlim = c(-5, 8),
                xlab = bquote(~Log[2]~ 'Fold Change'),#TODO What are the lables?
                ylab = bquote(~-Log[10]~ 'adjusted' ~italic(P))
                )

##Save Volcano Plot

dev.off()
png(filename = "./AshR Volcano Plot 41vs41.png",width = 11, height = 9, res = 300, units = "in")

ashrVPlot41vs41

par(mfrow = c(1,1)) 

dev.off()
```

#Session Info
```{r}
sink(file = "./SessionInfo.txt")
sessionInfo()
sink(file = NULL)
```



#References

The citation function can be used to  who you should be citing.

```{r}
#TODO
```

