---
title: "Isolating DE Genes from Expression analysis"
author: "Trevor Randall"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Clear Global Environment
```{r}
remove(list = ls())
```


```{r, include=TRUE}
#Set Library Directory
#PC Path
.libPaths(c("L:/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))

#Set working directory
#PC Path
setwd("E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/Analysis Temp X vs X/33vs37")
#Laptop Path
#Set Library Directory
#.libPaths(c(""))
#setwd("")
#sink(file = "./RSessionRawRun.txt") 
```


Libraries to open:
```{r}
library(readr)
library(VennDiagram)
```

Parapemers and Variables for Screening:
```{r}
#PAdjusted value to subset from data set
PAdjValue = 0.05

ColNameLablesDESeqTrevor <- c("locus", "baseMean", "log2FoldChange", "lfcSE", "stat", "pvalue", "padj")
```

Opening Datasets

```{r}
CF39_TDESeq_33vs37 <- read_delim("../../CF39vsCF39/CF39_33vs37/DESEQ Results/DESeqNew_results.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(CF39_TDESeq_33vs37) <- ColNameLablesDESeqTrevor

CF39S_TDESeq_33vs37 <- read_delim("../../CF39SvsCF39S/CF39S_33vs37/DESEQ Results/DESeqNew_results.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(CF39S_TDESeq_33vs37) <- ColNameLablesDESeqTrevor

LocusGeneAssociation <- read_csv("../Locus_GeneNamesAndPredictedFunction.csv")
```

#Add Gene info to the files based on locus:
```{r}
CF39_TDESeq_33vs37 <- merge(CF39_TDESeq_33vs37, LocusGeneAssociation, by = "locus")

CF39S_TDESeq_33vs37 <- merge(CF39S_TDESeq_33vs37, LocusGeneAssociation, by = "locus")

```

#Data Screening

Obtain DE Genes from the DESeq CF39_33vs37_TDESEQ Data

```{r}
CF39_33vs37_TDESEQ <- CF39_TDESeq_33vs37[((CF39_TDESeq_33vs37$padj <PAdjValue)& (!is.na(CF39_TDESeq_33vs37$padj))), ]

write.table(x = CF39_33vs37_TDESEQ, file="./CF39_33vs37_TDESEQ.txt", sep="\t", row.names=FALSE, col.names=colnames(CF39_33vs37_TDESEQ), quote=F)
```

Obtain DE Genes from the DESeq CF39S_33vs37 Data

```{r}
CF39S_33vs37_TDESEQ <- CF39S_TDESeq_33vs37[((CF39S_TDESeq_33vs37$padj <PAdjValue)& (!is.na(CF39S_TDESeq_33vs37$padj))), ]

write.table(x = CF39S_33vs37_TDESEQ, file="./CF39S_33vs37_TDESEQ.txt", sep="\t", row.names=FALSE, col.names=colnames(CF39S_33vs37_TDESEQ), quote=F)
```

#Data Comparisons

Comparison between CF39 and CF39S for the 33vs37 comparisons

```{r}
CF39_33vs37_Aly_TDES <- read_delim("./CF39_33vs37_TDESEQ.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

CF39S_33vs37_Aly_TDES <- read_delim("./CF39S_33vs37_TDESEQ.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

CF39_33vs37_SameGenes_TDE <- CF39_33vs37_Aly_TDES[(CF39_33vs37_Aly_TDES$locus %in% CF39S_33vs37_Aly_TDES$locus), ]

CF39_33vs37_DiffGenesToCF39S_TDE <- CF39_33vs37_Aly_TDES[!((CF39_33vs37_Aly_TDES$locus %in% CF39S_33vs37_Aly_TDES$locus)& (!is.na(CF39_33vs37_Aly_TDES$padj))), ]

CF39S_33vs37_DiffGenesToCF39_TDE <- CF39S_33vs37_Aly_TDES[!((CF39S_33vs37_Aly_TDES$locus %in% CF39_33vs37_Aly_TDES$locus)& (!is.na(CF39S_33vs37_Aly_TDES$padj))),]

write.table(x = CF39_33vs37_SameGenes_TDE, file="./Comparison/CF39_33vs37_SameGenes_TDE.txt", sep="\t", row.names=FALSE, col.names=colnames(CF39_33vs37_SameGenes_TDE), quote=F)

write.table(x = CF39_33vs37_DiffGenesToCF39S_TDE, file="./Comparison/CF39_33vs37_DiffGenesToCF39S_TDE.txt", sep="\t", row.names=FALSE, col.names=colnames(CF39_33vs37_DiffGenesToCF39S_TDE), quote=F)

write.table(x = CF39S_33vs37_DiffGenesToCF39_TDE, file="./Comparison/CF39S_33vs37_DiffGenesToCF39_TDE.txt", sep="\t", row.names=FALSE, col.names=colnames(CF39S_33vs37_DiffGenesToCF39_TDE), quote=F)

```

#Venn Comparison for the TDESeq comparison between CF39_33vs37 and CF39S_33vs37
```{r}
Number_33vs37_CF39 <- nrow(CF39_33vs37_Aly_TDES)
Number_33vs37_CF39S <- nrow(CF39S_33vs37_Aly_TDES)
CF39vsCF39S_Same <- nrow(CF39_33vs37_SameGenes_TDE)
```

```{r}
dev.off()

grid.newpage()
VD1 <- draw.pairwise.venn(area1 = Number_33vs37_CF39, area2 = Number_33vs37_CF39S,cross.area = CF39vsCF39S_Same, category = c("33vs37_CF39", "33vs37_CF39S"), lty = rep("blank", 2), fill = c("light blue", "pink"), alpha = rep(0.5, 2), cat.pos = c(-160, 160), cat.dist = rep(0.05, 2))

#Add a title
require(gridExtra)
grid.arrange(gTree(children=VD1), top="CF39_TDESeq to CF39S_TDESeq VennDiagram 33vs37")

dev.copy(png, filename = './VennDiagram/Venn33vs37_CF39vsCF39S.png', width=8, height=8, units="in",res=300)
dev.off()
```


#Session Info
```{r}
sink(file = "./SessionInfo.txt")
sessionInfo()
sink(file = NULL)
```


#Citations
```{r}
sink(file = "./SessionCitations.txt")

citation("VennDiagram")
citation("readr")
citation("gridExtra")

sink(file = NULL)
```

Venn Diagram Page: https://rstudio-pubs-static.s3.amazonaws.com/13301_6641d73cfac741a59c0a851feb99e98b.html?fbclid=IwAR1h2pL9V1tblTk4z9E1JX9udrel2ILE_WKKp2M8Kjd6HB0ZC6wwctFu61Y
