---
title: "Isolating DE Genes from Expression analysis"
author: "Trevor Randall"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Clear Global Environment
```{r}
remove(list = ls())
```

#Libraries to install:
```{r, eval=FALSE}
install.packages('VennDiagram')
```

# Accessing the Library and loading the read count table into the local environment

Since the remainder of the analysis does not differ in between Linux and Windows, the rest of the analysis was done in Windows. The first part of the actual analysis is to set the working directory. This can be done using the commands below:

```{r, include=TRUE}
#Set working directory
#PC Path
#Set Library Directory
.libPaths(c("L:/RStudios/RPackRatLibLocations", "L:/RStudios/RPackRat_2019_04_DESEQLibs"))
#Set working directory
#PC Path
setwd("E:/Dropbox/Dropbox/Harrison Lab - Trevor Randall/RNASeq Analysis/RNASeqAnlyPkrat_2020_03/CF39vsCF39S/41 vs 41/DE_Reg_Genes_Analysis/")
#Laptop Path
#Set Library Directory
#.libPaths(c(""))
#setwd("")
#sink(file = "./RSessionRawRun.txt") 
```


Libraries to open:
```{r}
library(readr)
#library(VennDiagram)
```


```{r}
ColNameLablesDESeqTrevor <- c("locus", "baseMean", "log2FoldChange", "lfcSE", "stat", "pvalue", "padj")
```


Opening Datasets

```{r}
TDESeq_41vs41 <- read_delim("../My DESEQ Script/DESeqNew_results.txt", "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(TDESeq_41vs41) <- ColNameLablesDESeqTrevor

LocusGeneAssociation <- read_csv("../../SourceRNASEQCountsForDESEQ/Locus_GeneNamesAndPredictedFunction.csv")
```

#Add Gene info to the files based on locus:
```{r}
TDESeq_41vs41 <-merge(TDESeq_41vs41, LocusGeneAssociation, by ="locus")

```

Parapemers for Screening:
```{r}
#PAdjusted value to subset from data set
PAdjValue = 0.05

#False discovery rate to screen for
FDRValue = 0.05
```

#Data Screening

Obtain DE Genes from the DESeq data that was parsed using the algorithem that Trevor set up:

```{r}
TDESEQ41vs41 <- TDESeq_41vs41[((TDESeq_41vs41$padj <PAdjValue)& (!is.na(TDESeq_41vs41$padj))), ]

write.table(x = TDESEQ41vs41, file="./TDESEQ41vs41.txt", sep="\t", row.names=FALSE, col.names=colnames(TDESEQ41vs41), quote=F)
```


#Session Info
```{r}
sink(file = "./SessionInfo.txt")
sessionInfo()
sink(file = NULL)
```


#Citations
```{r}
sink(file = "./SessionCitations.txt")

citation("VennDiagram")
citation("readr")
citation("gridExtra")

sink(file = NULL)
```

Venn Diagram Page: https://rstudio-pubs-static.s3.amazonaws.com/13301_6641d73cfac741a59c0a851feb99e98b.html?fbclid=IwAR1h2pL9V1tblTk4z9E1JX9udrel2ILE_WKKp2M8Kjd6HB0ZC6wwctFu61Y
